NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/appendix_modelDescription.tex
update supplemental material

\section{Appendix B: Code Example: Link Visualization with Model}
From the user's point of view, the following Python script is all the code the domain expert needs to link the NLP model with the visual interface and generate the tool used in the paper. The visualization library's API defines several callbacks (called Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.

>>>>

\section{Appendix B: Code Example: Link Visualization with Model}
From the user's point of view, the following Python script is all the code the domain expert needs to link the NLP model with the visual interface and generate the tool used in the paper. The visualization library's API defines several callbacks (called Hook in the code) that correspond to functions (e.g., prediction) need to be supplied by the NLP model.
